Implicit yaddayadda

### 2011-10-11 papers/PLDI2012/implicitization.tex
abstract interpretation, suite

\usepackage{amsmath,amsfonts}
\usepackage{mathcomp,amssymb}
\usepackage{dmnatbib}
\usepackage[mathscr]{euscript}
\usepackage{algorithmic,algorithm}

@@

Classically, one considers the control-flow graph of the program, with edges labeled with concrete transition relations (e.g. $x' = x+1$ for an instruction \lstinline|x = x+1;|), and attaches an abstract element to each control point.
A concrete transition relation $\tau \subseteq X \times X$ is replaced by an abstract \emph{forward abstract transformer} $\abstr{\tau}: \abstr{X} \rightarrow \abstr{X}$, such that
\begin{equation}
\forall \abstr{x} \in \abstr{X}, x,x' \in X,~
x \in \gamma(\abstr{x}) \land (x,x') \in \tau \implies
x' \in \gamma \circ \abstr{\tau}(\abstr{x})
\label{eqn:transformer_correct}
\end{equation}
It is easy to see that if to any control point $p \in P$ we attach an abstract element $\abstr{x}_p$ such that
(i) for any $p$, $\gamma(\abstr{x}_p)$ includes all initial states possible at control node $p$
(ii) for any $p,p'$, $\abstr{\tau}_{p,p'} (\abstr{x}_p) \sqsubseteq \abstr{x}_{p'}$, noting $\tau_{p,p'}$ the transition from $p$ to~$p'$, then $(\gamma(\abstr{x}_p))_{p \in P}$ form an \emph{inductive invariant}: by induction, the current program states always lie in $\gamma(\abstr{x}_p)$ at program location~$p$.

@@

The $\sigma$ function takes as parameters the index of the starting abstract
value, and the path we focus on. If we dynamically construct this function
during the analysis, we should store the results of the sigma function into a
compact representation, such as Algebraic Decision Diagrams.

>>>>

\usepackage{amsmath}
\usepackage{mathcomp,amsfonts,amssymb,MnSymbol}
\usepackage{dmnatbib}
\usepackage[mathscr]{euscript}
\usepackage{algorithmic,algorithm}

@@

Classically, one considers the control-flow graph of the program, with edges labeled with concrete transition relations (e.g. $x' = x+1$ for an instruction \lstinline|x = x+1;|), and attaches an abstract element to each control point.
A concrete transition relation $\tau \subseteq X \times X$ is replaced by an abstract \emph{forward abstract transformer} $\abstr{\tau}: \abstr{X} \rightarrow \abstr{X}$, such that
\begin{equation}
\forall \abstr{x} \in \abstr{X}, x,x' \in X,~
x \in \gamma(\abstr{x}) \land (x,x') \in \tau \implies
x' \in \gamma \circ \abstr{\tau}(\abstr{x})
\label{eqn:transformer_correct}
\end{equation}
It is easy to see that if to any control point $p \in P$ we attach an abstract element $\abstr{x}_p$ such that
(i) for any $p$, $\gamma(\abstr{x}_p)$ includes all initial states possible at control node $p$
(ii) for any $p,p'$, $\abstr{\tau}_{p,p'} (\abstr{x}_p) \sqsubseteq \abstr{x}_{p'}$, noting $\tau_{p,p'}$ the transition from $p$ to~$p'$, then $(\gamma(\abstr{x}_p))_{p \in P}$ form an \emph{inductive invariant}: by induction, the program states always lie in $\gamma(\abstr{x}_p)$ at program location~$p$.

\emph{Kleene iterations} compute such an inductive invariant as the stationary limit, if it exists, of the following system: for each $p$, initialize $\abstr{x}_p$ such that $\gamma(\abstr{x}_p)$ is a superset of the initial states at point $p$; then iterate the following: if $\abstr{\tau}_{p,p'} (\abstr{x}_p) \nsqsubseteq \abstr{x}_{p'}$, replace $\abstr{x}_{p'}$ by $\abstr{x}_{p'} \sqcup \abstr{\tau}_{p,p'} (\abstr{x}_p)$. Such a stationary limit is bound to exist if $\abstr{X}$ has no infinite ascending chain $a_1 \sqsubsetneq a_2 \sqsubsetneq \dots$; this condition is however not met by domains such as intervals or convex polyhedra.

@@

The $\sigma$ function takes as parameters the index of the starting abstract
value, and the path we focus on. If we dynamically construct this function
during the analysis, we should store the results of the sigma function into a
compact representation, such as Algebraic Decision Diagrams. Notice that the
image of a couple $(j,k)$ by the function $\sigma$ will be computed only if
needed.
